---
title: "arjas-gasbarra"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{arjas-gasbarra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dev.args = list(type = "cairo-png")
)
```

```{r setup}
library(bat)
```

The `simulate_study()` function is used to perform a single simulation.
A variety of treatment allocation rules are available to choose from.
Here's an example using the full Rule 2 form from Arjas & Gasbarra (2021):

```{r simulation}
set.seed(9082)
epsilon <- 0.1

results <- simulate_phase(
  phase(
    n = 240,
    rule = rule_2(
      epsilon = epsilon,
      epsilon_1 = 0.10,
      epsilon_2 = 0.05,
      theta_low = 0.10,
      delta = 0.1
    )
  ),
  a = 1,
  b = 1,
  theta = 0.2 + 1:4 / 10
)
```

The results keep track of the prior parameters and the prior probability of
being the best for each arm, as well as the arms' activity states and the
treatment allocation suggested by the rule for the next subject.

```{r results}
str(results)
```

It currently still takes some effort to visualize the results of the simulation:

```{r plotting, fig.height=6, fig.width=7}
# Plot results
with(results, {
  op <- par(mfrow = c(2, 1))
  
  # Posterior means
  mu <- a / (a + b)
  n <- seq_len(nrow(mu)) - 1
  
  par(mar = c(3, 5, 2, 1))
  matplot(
    n, mu,
    type = "l", lty = 1,
    xlab = "",
    ylab = expression(
      hat(theta[i])
    )
  )
  
  # Grey out estimates for inactive arms
  matlines(n, replace(mu, I, NA), col = "grey", lwd = 2, lty = 1)
  
  # Posterior probability of being being best
  par(mar = c(5, 5, 0, 1))
  matplot(
    n, p,
    type = "l", lty = 1,
    xlab = "# subjects",
    ylab = expression(
      "Pr(" * theta[i] * "=" * theta[v] * ")"
    )
  )
  abline(h = epsilon, col = "grey", lty = 2)
  
  par(op)
})
```

For the sake of comparison, here's the same study simulated using Thompson's
rule with $\kappa = 0.75$ as the treatment allocation procedure:

```{r thompson}
set.seed(1298)

results <- simulate_phase(
  phase(n = 240, rule = thompson(kappa = 0.75)),
  a = 1,
  b = 1,
  theta = 0.2 + 1:4 / 10
)
```

```{r plotting-thompson, fig.height=6, fig.width=7, echo=FALSE}
# Plot results
with(results, {
  op <- par(mfrow = c(2, 1))
  
  # Posterior means
  mu <- a / (a + b)
  n <- seq_len(nrow(mu)) - 1
  
  par(mar = c(3, 5, 2, 1))
  matplot(
    n, mu,
    type = "l", lty = 1,
    xlab = "",
    ylab = expression(
      hat(theta[i])
    )
  )
  
  # Grey out estimates for inactive arms
  matlines(n, replace(mu, I, NA), col = "grey", lwd = 2, lty = 1)
  
  # Posterior probability of being being best
  par(mar = c(5, 5, 0, 1))
  matplot(
    n, p,
    type = "l", lty = 1,
    xlab = "# subjects",
    ylab = expression(
      "Pr(" * theta[i] * "=" * theta[v] * ")"
    )
  )
  abline(h = epsilon, col = "grey", lty = 2)
  
  par(op)
})
```
