---
title: "Results in Arjas & Gasbarra (2021)"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{arjas-gasbarra}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 7,
  fig.height = 7,
  dev = "png",
  dev.args = list(type = "cairo-png")
)
```

```{r setup}
library(bat)
set.seed(20210520)
```

## Simulating a 2-arm trial: Experiment 1

Section 3.1.1 investigates the effect of different parameter combinations in Rule 1.
With {bat}, we can easily define the parameter combinations under investigation:

```{r parameters}
rules <- list(
  a = rule_1(delta = 0.10, epsilon = 0.10),
  b = rule_1(delta = 0.10, epsilon = 0.05),
  c = rule_1(delta = 0.05, epsilon = 0.20)
)

# Investigated hypotheses
theta_null <- c(0.3, 0.3)
theta_alt <- c(0.3, 0.5)
```

To create a single realization of a study, we can use `simulate_study()`:

```{r single-study}
study <- single_phase_study(n = 500, rule = rules[["a"]])
results <- simulate_study(study, a = 1, b = 1, theta = theta_alt)
```

The results track for each arm the prior parameters over time (`a` and `b`),
the probability of being the best (`p`), and the activity state (`I`).
Included is also the rule's next suggested allocation (`A`) , as well as the
simulated `data`. The used allocation rule is stored in the `"rule"` attribute.

```{r single-study-results}
str(results)
```

The `plot()` method gives us a simple summary of a single phase's results:

```{r single-study-plot}
plot(results)
```

For determining the operating characteristics of a set of design parameters,
we need to simulate multiple realizations of the same study. We'll do that for
the combinations of design parameters and hypotheses under investigation.

## Simulating a 4-arm trial: Experiment 2
